---
title: "Metaanalyses Review"
format: html
editor: visual
---

## Preparation

### Packages

```{r}
library(metafor)
```

### Working directory

```{r}
setwd("C:/Users/Data")
```

### Data

```{r}
CT <- read.csv2("C:/Users/Data/Detection_CT.csv")

EN <- read.csv2("C:/Users/Data/Detection_Endoscopy.csv")

Aidoc <- read.csv2("C:/Users/Data/AIDOC_TAT.csv")
```

### Aufbereitung

#### CT

```{r}
CT$n_noAI <- as.numeric(CT$n_noAI)
CT$M_noAI <- as.numeric(CT$M_noAI)
CT$SD_noAI <- as.numeric(CT$SD_noAI)
CT$n_AI <- as.numeric(CT$n_AI)
CT$M_AI <- as.numeric(CT$M_AI)
CT$SD_AI <- as.numeric(CT$SD_AI)

CT <- CT[with(CT, order(Study)), ]
```

#### Endoscopy

```{r}
EN <- EN[]

EN$n_noAI <- as.numeric(EN$n_noAI)
EN$M_noAI <- as.numeric(EN$M_noAI)
EN$SD_noAI <- as.numeric(EN$SD_noAI)
EN$n_AI <- as.numeric(EN$n_AI)
EN$M_AI <- as.numeric(EN$M_AI)
EN$SD_AI <- as.numeric(EN$SD_AI)

EN <- EN[with(EN, order(Study)), ]

```

#### Aidoc

```{r}

Aidoc$n_noAI <- as.numeric(Aidoc$n_noAI)
Aidoc$n_AI <- as.numeric(Aidoc$n_AI)

Aidoc <- Aidoc[with(Aidoc, order(Study)), ]
```

## Metaanalyse

### CT - Detection

Studies using AI for detection tasks in CT images that measured reading times of clinicians

Times in seconds

```{r}
dat <- escalc(measure = "SMD", m1i=M_AI, sd1i=SD_AI, n1i=n_AI, m2i=M_noAI, sd2i=SD_noAI, n2i=n_noAI,slab=Study, data=CT,  vtype="LS")
res <- rma(yi, vi, data=dat, method="DL", test ="knha", digits=2)
res

```

#### Forestplot

```{r}
### adjust the margins
par(mar=c(6,2.3,2.3,1.3), mgp=c(3,0,0), tcl=0.15)
dat$weights <- paste0(round(weights(res)), "%") # weights in % (rounded)


forest.rma(res, xlim=c(-20,8), at = c(-3,-2,-1,0,1,2,3),
       ilab=cbind(M_AI, SD_AI, M_noAI, SD_noAI), ilab.xpos=c(-9.5,-8,-6,-4.5),
       cex=0.85, header="Author(s) and Year",  shade = "zebra",  mlab="Random effects model summary (p = .30)")
op <- par(cex=0.85, font=2)
text(c(-9.5,-8,-6,-4.5), res$k+2, c("M", "SD", "M", "SD"), cex = 0.85)
text(c(-8.75,-5.25),     res$k+3,   c("With AI", "Without AI"), cex = 0.85)
par(font=2, cex = 0.85)
```

#### Funnel Plot

```{r}
funnel(res)
```

### Endoscopy

Studies using AI for detecting polyps during colonoscopy and measured the total procedure time

Times are in minutes

Levy, Nehme and Wang: M and SD had to be calculated from sample size, median and IQR using the method of Wan et al. \[1\]

```{r}
dat2 <- escalc("SMD", m1i=M_AI, sd1i=SD_AI, n1i=n_AI, m2i=M_noAI, sd2i=SD_noAI, n2i=n_noAI,slab=Study, data=EN,  vtype="LS", measure = "SMD")
res2 <- rma(yi, vi, data=dat2, method="DL", test ="knha", digits=2)
res2
```

#### Forestplot

```{r}
### adjust the margins
par(mar=c(6,3.2,2.3,1.3), mgp=c(3,0,0), tcl=0.15)

forest(res2, xlim=c(-16,8), at = c(-3,-2,-1,0,1,2,3),
       ilab=cbind(M_AI, SD_AI, M_noAI, SD_noAI), ilab.xpos=c(-9.5,-8,-6,-4.5),
       cex=0.85, header="Author(s) and Year",  shade = "zebra",  mlab="Random effects model summary (p = .87)")
op <- par(cex=0.85, font=2)
text(c(-9.5,-8,-6,-4.5), res2$k+2, c("M", "SD", "M", "SD"), cex = 0.85)
text(c(-8.75,-5.25),  res2$k+3, c("With AI", "Without AI"), cex = 0.85)
par(font=2, cex = 0.85)
```

#### Funnelplot

```{r}
funnel(res2)
```

## Priorization

Studies using AIDOC for ICH detection, report turnaround times for cases flagged positive

Times in minutes

SD calculated from CI: Seyam (2022) following the Cochrane Handbook \[2\]

```{r}
dat3 <- escalc("SMD", m1i=M_AI, sd1i=SD_AI, n1i=n_AI, m2i=M_noAI, sd2i=SD_noAI, n2i=n_noAI,slab=Study, data=Aidoc,  vtype="LS", measure = "SMD")
res3 <- rma(yi, vi, data=dat3, method="DL", test ="knha", digits=2)
res3
```

#### Forest Plot

```{r}
### adjust the margins
par(mar=c(6,3.2,2.3,1.3), mgp=c(3,0,0), tcl=0.15)

forest(res3, xlim=c(-16,6), at = c(-3,-2,-1,0,1,2,3),
       ilab=cbind(M_AI, SD_AI, M_noAI, SD_noAI), ilab.xpos=c(-9.5,-8,-6,-4.5),
       cex=0.85, header="Author(s) and Year",  shade = "zebra",  mlab="Random effects model summary (p = .84)")
op <- par(cex=0.85, font=2)
text(c(-9.5,-8,-6,-4.5), res3$k+2, c("M", "SD", "M", "SD"), cex = 0.85)
text(c(-8.75,-5.25),  res3$k+3, c("With AI", "Without AI"), cex = 0.85)
par(font=2, cex = 0.85)
```

#### Funnel Plot

```{r}
funnel(res3)
```

## References

1.  Wan X, Wang W, Liu J, Tong T. Estimating the sample mean and standard deviation from the sample size, median, range and/or interquartile range. BMC Med Res Methodol 2014;14:135. https://doi.org/10.1186/1471-2288-14-135.

2.  Higgins JP, Li T, Deeks JJ. Choosing effect measures and computing estimates of effect. In: Higgins JPT, Thomas J, Chandler J, Cumpston M, Li T, Page MJ, et al., editors. Cochrane Handb. Syst. Rev. Interv. 1st ed., Wiley; 2019, p. 143--76. https://doi.org/10.1002/9781119536604.ch6.
